OG_cleaning

### 2019-09-28 OG_cleaning.Rmd
added bit to get OG neg cells

filenames<-ls(pattern="summary.csv")
for(i in 1:16){
assign(filenames[i], data.frame(l[i]))}
```

@@

l<-lapply(ls(pattern="_OG"), function(x) get(x))
l<-lapply(l, function(x) sum_boolean(x))
l<-lapply(l, function(x) sum_boolean2(x))
filenames<-ls(pattern="_OG")
for(i in 1:9){
assign(filenames[i], data.frame(l[i]))}
```

@@

write.csv(OG_CD4_bulk_summary.csv, "OG_CD4_bulk_summary_clean.csv")
write.csv(OG_CD4_OG_summary.csv, "OG_CD4_OG_summary_clean.csv")
write.csv(OG_CD4_OG.GT_summary.csv, "OG_CD4_OG.GT_summary_clean.csv")
write.csv(OG_CD4_OG.IL4_summary.csv, "OG_CD4_OG.IL4_summary_clean.csv")
write.csv(OG_CD4_OG.TH1_summary.csv, "OG_CD4_OG.TH1_summary_clean.csv")
write.csv(OG_CD4_OG.TNFa_summary.csv, "OG_CD4_OG.TNFa_summary_clean.csv")
write.csv(OG_CD4_OG.IFNg_summary.csv, "OG_CD4_OG.IFNg_summary_clean.csv")

>>>>

filenames<-ls(pattern="summary.csv")
for(i in 1:17){
assign(filenames[i], data.frame(l[i]))}
```

@@

l<-lapply(ls(pattern="_OG"), function(x) get(x))
l<-lapply(l, function(x) sum_boolean(x))
l<-lapply(l, function(x) sum_boolean2(x))
filenames<-ls(pattern="_OG")
for(i in 1:10){
assign(filenames[i], data.frame(l[i]))}

OG_CD4_noOG_summary.csv<-sum_boolean(OG_CD4_noOG_summary.csv)
OG_CD4_noOG_summary.csv<-sum_boolean2(OG_CD4_noOG_summary.csv)
```

@@

write.csv(OG_CD4_bulk_summary.csv, "OG_CD4_bulk_summary_clean.csv")
write.csv(OG_CD4_OG_summary.csv, "OG_CD4_OG_summary_clean.csv")
write.csv(OG_CD4_OG.GT_summary.csv, "OG_CD4_OG.GT_summary_clean.csv")
write.csv(OG_CD4_OG.IL4_summary.csv, "OG_CD4_OG.IL4_summary_clean.csv")
write.csv(OG_CD4_OG.TH1_summary.csv, "OG_CD4_OG.TH1_summary_clean.csv")
write.csv(OG_CD4_OG.TNFa_summary.csv, "OG_CD4_OG.TNFa_summary_clean.csv")
write.csv(OG_CD4_OG.IFNg_summary.csv, "OG_CD4_OG.IFNg_summary_clean.csv")
write.csv(OG_CD4_noOG_summary.csv, "OG_CD4_noOG_summary_clean.csv")
